Solutions to Integer Programming from Quantum Annealing

### 2020-03-12 paper/main.tex
add qubo reference

\affil[1]{RIKEN Interdisciplinary Theoretical and Mathematical Sciences (iTHEMS), Wako, Saitama 351-0198, Japan}
\affil[1]{Department of Physics, University of California, Berkeley, California 94720, USA}
\affil[1]{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
\affil[2]{?}
\affil[3]{Department of Physics, University of California, Berkeley, California 94720, USA}
\affil[4]{Quantum Computing Institute, Oak Ridge National Laboratory, Oak Ridge, Tennessee 37831, USA}
\affil[4]{University of Tennessee}
\affil[*]{ckoerber@berkeley.edu}

@@

Quantum annealing solves a general quadratic binary optimization problem (QUBO) by slowly varying a time-dependent Hamiltonian~\cite{}. Through the adiabatic theorem of quantum mechanics, the annealer is prepared initially in a trivial ground state while the solution to ILP is encoded in the target Hamiltonian. Due to the explosion in research efforts towards hardware implementations of quantum annealers and future improvements to the annealing schedule~\cite{}, mapping ILP to QUBO provides a path forward towards obtaining optimal solutions to the class of integer optimization problems.

>>>>

\affil[1]{Department of Physics, University of California, Berkeley, California 94720, USA}
\affil[1]{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
\affil[2]{RIKEN Interdisciplinary Theoretical and Mathematical Sciences (iTHEMS), Wako, Saitama 351-0198, Japan}
\affil[2]{Department of Physics, University of California, Berkeley, California 94720, USA}
\affil[3]{R\&D Group, Grid Inc., Tokyo 107-0061, Japan}
\affil[4]{Quantum Computing Institute, Oak Ridge National Laboratory, Oak Ridge, Tennessee 37831, USA}
\affil[4]{University of Tennessee}
\affil[*]{ckoerber@berkeley.edu}

@@

Quantum annealing solves a general quadratic binary optimization problem (QUBO) by slowly varying a time-dependent Hamiltonian~\cite{}. Through the adiabatic theorem of quantum mechanics, the annealer is prepared initially in a trivial ground state while the solution to ILP is encoded in the target Hamiltonian. Due to the explosion in research efforts towards hardware implementations of quantum annealers and future improvements to the annealing schedule~\cite{}, mapping ILP to QUBO provides a path forward towards obtaining optimal solutions to the class of integer optimization problems~\cite{2018Glover}.
